The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-05-21 ms.Rmd
tidying up and re-running higher res Feng_Papes workflow

<!--
covariates Feng & Papes used:
1    annual mean temperature
2    mean diurnal range
3    isothermality
4    temperature seasonality
6    minimum temperature of the coldest month
9    mean temperature of the driest quarter
10   mean temperature of the warmest quarter
12   annual precipitation
15   precipitation seasonality
-->

<!---
Notes:

-->

@@

```{r fengworkflow, eval = TRUE, dpi = 300, fig.show = 'hide', results = 'hide', message = FALSE}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = PrintMap)

>>>>

@@

```{r fengworkflow, eval = TRUE, dpi = 300, fig.show = 'hide', results = 'hide', message = FALSE, fig.height = 9, fig.width = 9}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = PrintMap)
```
